Computer-Assisted Analysis of the \\ Anderson-Hájek Ontological Controversy

### 2015-07-13 Papers/InProgress/HajekAndersonControversy/main.tex
Fix typo

He takes the property of being God-like as a primitive and defines (B:D1) the positive properties as
those properties necessarily possessed by every God-like being. He
then briefly indicates (B:L1) that B:D1 is logically equivalent, under
modal logic \SFour, to the conjunction of D1', A2', A3' and A4'. This
has been confirmed in the computer-assisted formalization: A2' and A3'
can be quickly automatically derived in logic \K. A4' can be proved in
logic \KT (i.e. assuming reflexivity of the accessibility relation).
For constant domain semantics, proving D1' is possible in logic \KFour,
whereas for varying domain semantics, a counter model can be found
even in logic \SFive. Conversely, the proof that B:D1 is entailed by
D1', A2', A3' and A4' is possible already in logic \K. The provers
also show that theorem T3' follows from B:D1, B:D2, B:D3, A:A1' and
A5' already in logic \KB. Bjordal's last paragraph briefly mentions
Hájek's ideas about the superfluousness of A5' and claims that it is
possible, with (unclear) additional modifications of the definitions,
to eliminate A5' from his theory as well. Without any additional
modification, the automated reasoners show that A5' is actually not
superfluous. All these results, with the exception of the
aforementioned countermodel for D1', hold for both constant and
varying domain semantics.

>>>>

He takes the property of being God-like as a primitive and defines (B:D1) the positive properties as
those properties necessarily possessed by every God-like being. He
then briefly indicates (B:L1) that B:D1 is logically equivalent, under
modal logic \SFour, to the conjunction of D1', A2', A3' and A4'. This
has been confirmed in the computer-assisted formalization: A2' and A3'
can be quickly automatically derived in logic \K. A4' can be proved in
logic \KT (i.e. assuming reflexivity of the accessibility relation).
For constant domain semantics, proving D1' is possible in logic \KFour,
whereas for varying domain semantics, a countermodel can be found
even in logic \SFive. Conversely, the proof that B:D1 is entailed by
D1', A2', A3' and A4' is possible already in logic \K. The provers
also show that theorem T3' follows from B:D1, B:D2, B:D3, A:A1' and
A5' already in logic \KB. Bjordal's last paragraph briefly mentions
Hájek's ideas about the superfluousness of A5' and claims that it is
possible, with (unclear) additional modifications of the definitions,
to eliminate A5' from his theory as well. Without any additional
modification, the automated reasoners show that A5' is actually not
superfluous. All these results, with the exception of the
aforementioned countermodel for D1', hold for both constant and
varying domain semantics.
